Hydras \& Co.

### 2023-10-13 doc/chapter-primrec.tex
sart a new chapter on Goedel encoding (after Russel)
work on the chapter on goedel encodings; new exercise
add a missing citation
New notations (#139)
* experiment fol notations

* first attempts

* experiment FOL notations

* experiment FOL notations

* minor change

* minor change

* minor change

* experimental notations

* experimental notations

* minor changes, bullets in folLogic

* bulletizing folLogic.v (half done, to resume at forallE)

* bulletized folLogic.v

* Example of folLogic

* more examples

* drinkers theorem in FOL (clumsy draft)

* re-structuring prro scripts in folLogic2

\begin{remark}
 The theory of primitive recursive function is now hosted in
the \texttt{theories/ordinals/Ackermann} directory.
The specific part on G\"odel's theorem,  is also on
coq-community (\url{https://github.com/coq-community/goedel}) and requires the 
\href{https://github.com/coq-community/pocklington}{Pocklington library} for lemmas on primality.
\end{remark}

@@

\index{primrec}{Types!naryFunc}
\input{movies/snippets/extEqualNat/naryFunc.tex}

@@

\index{primrec}{Predicates!extEqual}

@@

\index{primrec}{Types!PrimRec}
\index{primrec}{Types!PrimRecs}
\label{def:Primrec}
\vspace{4pt}
\noindent
\emph{From \href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec}.}

@@

\index{primrec}{Functions!evalPrimRec}
\index{primrec}{Functions!evalPrimRecs}

@@

\index{primrec}{Predicates!isPR}
%\index{coq}{Extensionally equal functions}

@@

\index{primrec}{Exercises}
\begin{exercise}
There is a lot of lemmas similar to \texttt{filter010IsPR} in the \texttt{primRec} library, useful to control the arity of functions.
Thus, the reader may look at them, and invent simple examples of application for each lemma.
\end{exercise}

\index{primrec}{Exercises}
\begin{exercise}
Multiplication of natural number is already proven in the \texttt{primRec} library. Write a proof of your own, then compare to the library's version.
\end{exercise}

@@

\index{primrec}{Exercises}
\begin{exercise}
Prove that the following functions are primitive recursive.

@@

\index{primrec}{Exercises}
\begin{exercise}
Show that the function \texttt{min: naryFunc\,2} is primitive
recursive.

@@

\index{primrec}{Exercises}

@@

@@

\index{primrec}{Exercises}
\begin{exercise}

@@

\vspace{4pt}
\noindent
\emph{From \href{../theories/html/hydras.MoreAck.Ack.html}{MoreAck.Ack}}.
\index{maths}{Ackermann function}
\index{primrec}{Ackermann function}

@@

>>>>

@@

\index{ackermann}{Types!naryFunc}
\input{movies/snippets/extEqualNat/naryFunc.tex}

@@

\index{ackermann}{Predicates!extEqual}

@@

\index{ackermann}{Types!PrimRec}
\index{ackermann}{Types!PrimRecs}
\label{def:Primrec}
\vspace{4pt}
\noindent
\emph{From \href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec}.}

@@

\index{ackermann}{Functions!evalPrimRec}
\index{ackermann}{Functions!evalPrimRecs}

@@

\index{ackermann}{Predicates!isPR}
%\index{coq}{Extensionally equal functions}

@@

\index{ackermann}{Exercises}
\begin{exercise}
There is a lot of lemmas similar to \texttt{filter010IsPR} in the \texttt{primRec} library, useful to control the arity of functions.
Thus, the reader may look at them, and invent simple examples of application for each lemma.
\end{exercise}

\index{ackermann}{Exercises}
\begin{exercise}
Multiplication of natural number is already proven in the \texttt{primRec} library. Write a proof of your own, then compare to the library's version.
\end{exercise}

@@

\index{ackermann}{Exercises}
\begin{exercise}
Prove that the following functions are primitive recursive.

@@

\index{ackermann}{Exercises}
\begin{exercise}
Show that the function \texttt{min: naryFunc\,2} is primitive
recursive.

@@

\index{ackermann}{Exercises}

@@

\emph{See also the chapter~\ref{chap:encoding} on G\"{o}del's encodings.}

@@

\index{ackermann}{Exercises}
\begin{exercise}

@@

\vspace{4pt}
\noindent
\emph{From \href{../theories/html/hydras.MoreAck.Ack.html}{MoreAck.Ack}}.
\index{maths}{Ackermann function}
\index{ackermann}{Ackermann function}

@@

\subsection{Related work}

This proof is very close to the 1993 proof by Nora Szasz with the \texttt{Alf} proof assistant~\cite{Szasz93}. This proof has also been adapted
by Lawrence C. Paulson to Isabelle/HOL~\cite{paulson_2021}.
